\begin{thebibliography}{99}

\bibitem{booch-uml}
G.~Booch, J.~Rumbaugh, and I.~Jacobson,
\textit{The Unified Modeling Language User Guide}, 2nd~ed.
Addison-Wesley, 2005.

\bibitem{sommerville-se}
I.~Sommerville,
\textit{Software Engineering}, 10th~ed.
Pearson, 2016.

\bibitem{moscow-ieee}
K.~S.~Ahmad, K.~S.~Ahmad, and A.~Sana,
``Fuzzy\_MoSCoW: A fuzzy based MoSCoW method for the prioritization of software requirements,''
in \textit{Proc. IEEE Int. Conf. on Computing, Mathematics and Engineering Technologies (iCoMET)},
Sukkur, Pakistan, 2018, pp.~1--5.
doi: \texttt{10.1109/ICOMET.2018.8342602}

\bibitem{k8s-concepts}
The Kubernetes Authors,
``Kubernetes Concepts,''
Kubernetes Documentation, 2024.
[Online]. Available: \url{https://kubernetes.io/docs/concepts/}
[Accessed: May 2025].

\bibitem{k8s-autoscaling}
The Kubernetes Authors,
``Autoscaling Workloads,''
Kubernetes Documentation, 2025.
[Online]. Available: \url{https://kubernetes.io/docs/concepts/workloads/autoscaling/}
[Accessed: May 2025].

\bibitem{k8s-hpa}
The Kubernetes Authors,
``Horizontal Pod Autoscaling,''
Kubernetes Documentation, 2025.
[Online]. Available: \url{https://kubernetes.io/docs/tasks/run-application/horizontal-pod-autoscale/}
[Accessed: May 2025].

\bibitem{kubecost-vpa}
Kubecost Team,
``The Guide to Kubernetes VPA by Example,''
Kubecost Blog, 2025.
[Online]. Available: \url{https://www.kubecost.com/kubernetes-autoscaling/kubernetes-vpa/}
[Accessed: May 2025].

\bibitem{k8s-hpa-vpa-conflict}
Ksolves,
``Kubernetes Autoscaling: HPA vs.\ VPA vs.\ Cluster Autoscaler,''
Ksolves Blog, 2025.
[Online]. Available: \url{https://www.ksolves.com/blog/devops/kubernetes-autoscaling-hpa-vs-vpa-vs-cluster-autoscaler}
[Accessed: May 2025].

\bibitem{multitenant-cloud}
R.~Yahyapour \textit{et al.},
``Multi-tenancy: Deep dive on how cloud platforms serve many customers,''
\textit{World Journal of Advanced Research and Reviews (WJARR)},
vol.~26, no.~1, 2025.
[Online]. Available: \url{https://journalwjarr.com/sites/default/files/fulltext_pdf/WJARR-2025-1608.pdf}
[Accessed: May 2025].

\bibitem{microsoft-tenancy}
Microsoft,
``Tenancy Models for a Multitenant Solution,''
Azure Architecture Center, Microsoft Learn, 2024.
[Online]. Available: \url{https://learn.microsoft.com/en-us/azure/architecture/guide/multitenant/considerations/tenancy-models}
[Accessed: May 2025].

\end{thebibliography}